\documentclass[a4paper]{article}

\usepackage{textcomp}
\usepackage{array}


\title{Personal Resum\'e}
\author{Matthew Signorini}

\usepackage[pdftex,bookmarks,colorlinks]{hyperref}

\begin{document}

\maketitle

\section{Personal Details}
\begin{tabular}{>{\raggedright}m{3cm} l}
    \textbf{Full Name} &Matthew Peter Signorini\\
 \textbf{Address} &12 Winjallock Crescent, Vermont South 3133\\
\textbf{Home Ph.} &(03) 9801 5013\\
    \textbf{E-mail} &\texttt{matt@signorini.id.au}\\
    \textbf{Github} &\url{https://github.com/pkill-9}
\end{tabular}


\section{Previous Employment}
\begin{description}
    \item[2016 -- present] Software Engineer at Ayuda Hosting. My tasks
        are mainly oriented around maintaining PHP web applications,
        including a CMS that was developed in house. I am also involved in
        tasks around our hosting infrastructure, where I have gained
        experience maintaining linux servers managed by puppet, and Xen
        virtualisation. I have also gained experience of Nagios, and I am
        on a roster for after hours response to technical problems.
    \item[2014 -- 2016] Casual tutor at the University of Melbourne. I
        have taught two introductory C programming subjects, which requires
        me to assist students who are confused or stuck on a programming
        problem, as well as managing the class in general.
    \item[2013 -- 2014] I worked for Ourcast during the summer break from
        university as a server side software engineering intern. My role
        included developing prototype machine learning algorithms to filter
        out false positives from rain radar images, prototyped in GNU 
        Octave. I also contributed to creating a program in Java to produce
        rain predictions on a radar station by station basis, and also code
        to measure the accuracy of the predictions. I found that my
        experience with Linux was very useful in this job, particularly when
        it came to using SSH and terminal commands, which I am well accustomed
        to.
    \item[2006 -- present] I am employed as the audio technician for Box
        Hill Ballet Association's end of year concert. Initially, this 
        involved a significant learning curve, as I had little experience 
        in operating an audio desk when I first started. This also involves 
        working as part of a team with the rest of the backstage crew, and
        following instructions from the stage manager.
    \item[2004 -- 2008] I Delivered daily newspapers for Vermont South
        Newsagency. This required attendance at 6:00 am, and attention to
        detail.
    \item[2011 -- 2014] I also delivered pamphlets on a casual/contract
        basis for Salmat.
\end{description}


\section{Education}
\begin{tabular}{>{\raggedright}m{3cm} l}
    \textbf{2013 -- 2015} &The University of Melbourne, \\
                             &Masters of Science (Computer Science)\\
    \textbf{2010 -- 2013} &The University of Melbourne, \\
                             &Bachelor of Science (Computer Science)\\
    \textbf{2004 -- 2009} &Vermont Secondary College\\
           \textbf{ENTER} &91.05\\
    \textbf{1998 -- 2003} &Vermont Primary School\\
    \textbf{1997 -- 1998} &Boronia West Primary School\\
\end{tabular}


\section{Summary of Skills}
\begin{description}
    \item[\LaTeX{}] I am experienced with using the \LaTeX{} typesetting
        system, with which this document was prepared.
    \item[Linux/UNIX] I have had Ubuntu Linux installed on my PC since
        2008. As part of my course at university, I have also learnt to
        use Unix (Solaris in this case), where we were taught to use an
        SSH client, bash commands, and using the Vim editor. As a result,
        I have extensive knowledge of Linux and Unix.
    \item[Programming languages] I have had extensive experience writing
        programs in C, with projects including a multithreaded POP3 email 
        server, and a FAT32 file system driver. I also have extensive
        experience with object oriented programming in Java, and a limited
        knowledge of C++, C\# and Python. I have also learnt
        bash shell script, using it mainly for running tests on programs
        written for university assessment tasks. I do have a good
        knowledge of assembly language, particularly x86 but also others
        such as the RISC language used by Atmel microcontrollers.
    \item[Version control systems] I was taught to use Subversion as part
        of my university course, and have also learned to use Mercurial,
        which I use to track most of my personal projects. I have extensive
        experience with both of these tools, including setting up
        repositories, and checking in and out, both locally, and over a
        network.
    \item[Bicycle Maintenance] Including reasonably advanced tasks: I have
        taught myself how to build bicycle wheels, and I have pulled
        apart a dynamo hub, and also two different types of hub gear: a
        three speed Sturmey-Archer hub, and also a 14 speed Rohloff hub.
        I successfully reassembled all of these to working order. The
        Rohloff hub was quite an interesting exercise, because I managed
        to demonstrate a technique that I developed which eliminates a
        particularly fiddly step in the reassembly.
\end{description}


\section{Voluntary Work}
As a member of the Melbourne Bicycle Touring Club, I have helped out
at events the club has organised where volunteers were needed, and I have
served on the committee (in various roles) from 2014 to 2017. Part of my
role while on the committee was to run club meetings, which at that time
were held every two weeks.

Boronia Church of Christ runs a caf\'e called ``The Hub'', where I have
spent time helping out. As part of my work there I learnt to
operate an espresso machine. I 
also operated the data projector and audio desk on a roster for Sunday 
morning church services (typically once or twice a month).

While I was at primary school and high school I also helped out at
numerous school working bees, mainly doing gardening work.


\section{Hobbies and Interests}
I love outdoor activities such as cross country skiing, cycling
and camping. I have already mentioned my involvement with the MBTC, and I
regularly go on day rides and camping trips with the club. I have
also organised and led a number of rides.

I have published several software projects that I have written in my
spare time on my github and bitbucket profiles, which can be found at
\url{https://github.com/pkill-9} and \url{https://bitbucket.org/void-star}
respectively. Among other things, I am interested in operating systems,
especially microkernels such as \textsc{minix}. One ongoing project I am
working on is to test an idea that I have had about sharing memory between
different processes by page aliasing, where the same chunk of physical 
memory is mapped into the virtual address spaces of two different processes.
This could be faster than the current technique, where the kernel must
copy data from one process to another.
I have also read the book
``Clean code'' by Robert C. Martin, and take an interest in producing clean
code myself.


% TODO: adjust academic interests to include research project topic. Also
% bring back electronics/arduino, including bike speedo project.


\section{Referees}
Glenn Wilson, Ayuda Hosting\\
Email: \texttt{glenn@ayuda.com.au}; Phone: 0412 125 960\\ \\
John Harland, President of Melbourne Bicycle Touring Club 2014 -- 2016\\
Email: \texttt{harland.john@gmail.com}\\ \\
Written reference from Vermont South Newsagency.


\end{document}

% vim: ft=tex ts=4 sw=4 et
